\documentclass[11pt]{exam}

\usepackage{amsmath} % allows for align environment
\usepackage{amssymb} % 
\usepackage{array} % for table alignments

% FONT FORMAT
% \renewcommand*\rmdefault{ppl} % change font to Palatino
\renewcommand*\rmdefault{lmss} % change font to lat mod ss

% ADJUST MARGINS
\usepackage[bmargin=1.0in]{geometry}
\geometry{margin=1in}
\geometry{tmargin=1in}

\begin{document}

\begin{center}
    \Large MATH 1554 QH \\[2pt] Written Assignment 2
\end{center}
\thispagestyle{empty} % suppress page numbering

    
\noindent Please \textbf{show your work} for each of the questions below.

\begin{questions}

    \question[5] Consider the matrix $A$ and vector $b$ below.
    $$A = \begin{pmatrix} 4&3&0\\3&2&1\\0&1&2 \end{pmatrix}, \quad b = \begin{pmatrix} 7\\8\\3\end{pmatrix}$$
    The goal of this exercise is to solve the system $Ax=b$ using the LU factorization, where $x \in \mathbb R^3$.
    \begin{parts}
        \part Construct the LU-factorization of matrix $A$. Use at most two row operations to compute $U$.
        \part Let $y = Ux$. Use your factorization to solve $Ly=b$ for vector $y$.
        \part Use your vector $y$ from the previous part to solve $Ux=y$.
    \end{parts}
    
    Note that although you are not asked to do so, we recommend confirming that the product $LU$ equals the given $A$ matrix for your $L$ and $U$. Likewise, you can check your work for parts b and c by solving $Ax=b$ without the LU factorization and comparing your results. It isn't necessary to perform these additional calculations, but they can help you check that your work is correct. 

    \question[5] Triangle $S$ is determined by the points $P(1,1), Q(3,1), R(1,2)$. Transform $T$ rotates points counterclockwise about the point $(0,1)$ by $\pi/2$ radians. 
    \begin{parts}
        \part Represent the three data points with a matrix, $D$. Use homogeneous coordinates. 
        \part Construct the standard matrix $A$, so that $T_A(\vec x)=A\vec x$ rotates points about the given point. Use homogeneous coordinates. Express $A$ as a single $3\times 3$ matrix. 
        \part Use matrix multiplication to determine the image of $S$ under $T$. 
        \part Clearly state the coordinates of the triangle after the transformation. 
    \end{parts}
    Note that although you are not asked to do so, we recommend confirming that your work is correct by plotting the points before and after the transform. 
\end{questions}


\noindent Please ensure that you follow the instructions below. 
\begin{itemize}
    \item Your work is legible in the files you uploaded. 
    \item Questions are answered in the order in which they were given. 
    \item During the upload process, you indicated which pages correspond to which question.
    \item During the upload process that none of your pages are upside down or sideways. 
    \item Each question is answered on its own page (or pages). 
    \item Your work is submitted as a single PDF file.
    \item You uploaded your work to the correct location in Gradescope (in other words, make sure that you upload your work for this assignment to the correct assignment).
\end{itemize}
\noindent Note that
\begin{itemize}
    \item A small amount of points (at most 1 point) will be deducted from the assignment for not following the instructions listed above. 
    \item You can also change the orientation of the pages when you upload in Gradescope. 
    \item Ensuring that these criteria are met helps ensure that your work is graded efficiently and accurately. 
\end{itemize}

\end{document}
